Quantifying the dominance and commoness of ESVs

### 2020-11-19 exploratory/2020-09-09-genome-sens-spec.Rmd
Combine count tibble files, closes #34

```{r}
count_tibble <- read_tsv(here("data/processed/rrnDB.esv.count_tibble"),
												 col_types = "cccd")
```

@@

```{r}
count_tibble %>%
	group_by(region, esv) %>%
	summarize(n_genomes = n()) %>%
	count(n_genomes) %>%
	mutate(fraction = n/sum(n)) %>%
	filter(n_genomes == 1)
```

>>>>

```{r}
count_tibble <- read_tsv(here("data/processed/rrnDB.easv.count_tibble"),
								col_types = cols(.default = col_character(),
																 count = col_integer())) %>%
	filter(threshold == "esv") %>%
	select(-threshold)
```

@@

```{r}
count_tibble %>%
	group_by(region, easv) %>%
	summarize(n_genomes = n()) %>%
	count(n_genomes) %>%
	mutate(fraction = n/sum(n)) %>%
	filter(n_genomes == 1)
```

### 2020-11-19 exploratory/2020-09-29-taxa-representation.Rmd
Combine count tibble files, closes #34

esv <- read_tsv(here("data/processed/rrnDB.esv.count_tibble"),
								col_types = cols(.default = col_character(),
																 count = col_integer()))

>>>>

esv <- read_tsv(here("data/processed/rrnDB.easv.count_tibble"),
								col_types = cols(.default = col_character(),
																 count = col_integer())) %>%
	filter(threshold == "esv") %>%
	select(-threshold)

### 2020-11-19 exploratory/2020-10-15-esv-species-coverage.Rmd
Combine count tibble files, closes #34

species_esvs <- metadata_esv %>%
	select(genome_id, species, region, esv, count) %>%
	group_by(region, species) %>%
	summarize(n_genomes = n_distinct(genome_id),
						n_esvs = n_distinct(esv),
						n_rrns = sum(count) / n_genomes,
						esv_rate = n_esvs/n_genomes,
						.groups="drop")

>>>>

species_esvs <- metadata_esv %>%
	select(genome_id, species, region, easv, count) %>%
	group_by(region, species) %>%
	summarize(n_genomes = n_distinct(genome_id),
						n_esvs = n_distinct(easv),
						n_rrns = sum(count) / n_genomes,
						esv_rate = n_esvs/n_genomes,
						.groups="drop")

### 2020-11-19 exploratory/2020-10-21-esv-taxa-overlap.Rmd
Combine count tibble files, closes #34

	# metadata_esv - input data
	overlap_data <- inner_join(metadata_esv, subsampled_genomes, by="genome_id") %>%
	# - focus on taxonomic ranks - kingdom to species, esv, and region
		select(-genome_id, -count, -strain) %>%
	# - make data frame tidy
		pivot_longer(cols=c(-region, -esv), names_to="rank", values_to="taxon") %>%
	# - remove lines from the data where we don't have a taxonomy
		drop_na(taxon) %>%
	# - remove redundant lines
		distinct() %>%
	# for each region and taxonomic rank, group by esvs
		group_by(region, rank, esv) %>%
	# - for each esv - count the number of taxa
		summarize(n_taxa = n(), .groups="drop_last") %>%
	# - count the number of esvs that appear in more than one taxa
		count(n_taxa) %>%
	# - find the ratio of the number of esvs in more than one taxa to the total number of esvs
		summarize(overlap = sum((n_taxa > 1) * n) / sum(n), .groups="drop") %>%
		mutate(rank = factor(rank, levels=c("kingdom", "phylum", "class", "order", "family", "genus", "species"))) %>%
		mutate(overlap = 100*overlap)

>>>>

	# metadata_esv - input data
	overlap_data <- inner_join(metadata_esv, subsampled_genomes, by="genome_id") %>%
	# - focus on taxonomic ranks - kingdom to species, esv, and region
		select(-genome_id, -count, -strain) %>%
	# - make data frame tidy
		pivot_longer(cols=c(-region, -easv), names_to="rank", values_to="taxon") %>%
	# - remove lines from the data where we don't have a taxonomy
		drop_na(taxon) %>%
	# - remove redundant lines
		distinct() %>%
	# for each region and taxonomic rank, group by esvs
		group_by(region, rank, easv) %>%
	# - for each easv - count the number of taxa
		summarize(n_taxa = n(), .groups="drop_last") %>%
	# - count the number of esvs that appear in more than one taxa
		count(n_taxa) %>%
	# - find the ratio of the number of esvs in more than one taxa to the total number of esvs
		summarize(overlap = sum((n_taxa > 1) * n) / sum(n), .groups="drop") %>%
		mutate(rank = factor(rank, levels=c("kingdom", "phylum", "class", "order", "family", "genus", "species"))) %>%
		mutate(overlap = 100*overlap)

### 2020-11-19 exploratory/2020-11-02-dominance-commonness-of-esvs.Rmd
Combine count tibble files, closes #34

n_genomes_rrn_copies_per_species <-
	metadata_esv %>%
	# need the counts by region and by genome for each species
  select(region, genome_id, species, esv, count) %>%
	# group our ESVs by region and species
  group_by(region, species) %>%
  summarize(
  	# number of distinct genomes per region/species
  	n_genomes = n_distinct(genome_id),
  	# summing up the number of 16S rRNA copies across all genomes for
  	# a species and region and divide by number of genomes
  	mean_rrns = sum(count) / n_genomes,
  	.groups="drop"
  )

@@

	# want to do our analysis for the species level for each region of 16S will
	# want to group our genomes by ESVs and species to count the number of genomes
	# that each ESV appears in
  select(region, genome_id, species, esv, count) %>%
  group_by(region, species, esv) %>%

>>>>

n_genomes_rrn_copies_per_species <-
	metadata_esv %>%
	# need the counts by region and by genome for each species
  select(region, genome_id, species, easv, count) %>%
	# group our ESVs by region and species
  group_by(region, species) %>%
  summarize(
  	# number of distinct genomes per region/species
  	n_genomes = n_distinct(genome_id),
  	# summing up the number of 16S rRNA copies across all genomes for
  	# a species and region and divide by number of genomes
  	mean_rrns = sum(count) / n_genomes,
  	.groups="drop"
  )

@@

	# want to do our analysis for the species level for each region of 16S will
	# want to group our genomes by ESVs and species to count the number of genomes
	# that each ESV appears in
  select(region, genome_id, species, easv, count) %>%
  group_by(region, species, easv) %>%
